\documentclass[titlepage]{article}

\author{ Dispoto, Brett\\
	\and
	Kamel, Adham\\
	\and
	Cai, Feiyu\\
}

\title{CS157A Project Proposal}

\begin{document}
	\maketitle
	
	\section{Project Overview}	
	%----------------------------------------Adham fill in here--------------------------
	%Provide descriptions of the three-tier Based Database Application your team will be developing. Who are stakeholders? Why is it important?   	
	



	\section{System Enviroment}
	%----------------------------------------Brett fill in here--------------------------
	%A Structure Diagram of the system (graph/diagra based on 3-tier architecture)HW/SW used RDBMS Used (MySQL) Programming/Application languages used (Java, Java Script,  XML, SQL, etc)	


	
	\section{Functional Requirements}
	The system will provide searching, sorting the shown book lists, reading, reading reviews, and sharing via email functions from our free textbook database. 
	Anonymous visitors can use these functions without sign up for an account. However, signing up for an account with a valid email address will provide more functions. 
	A user can sign in his/her account with his/her email address and password. A sign in user will have additional functions such as writing reviews, 
	set favorites books and have access to their account detail page. 
	

	Reading: reading the books itself or its reviews. Input: book information. Output: book content


	Searching: searching for book from the provided information. Input: title, author, year of publication, publisher, ISBN, genre, etc. Output: book details.
	
	
	Sorting: sort the way books are listed. Input: sorting rules such as reviews, alphabetical order, etc.
	
	
	Review: Give a review and write comments for a book. Input: review and comments. Output: Review and comments are posted on the database that everyone can see
	
	
	Set favorites: set a book as favorites, the user can see it in his/her profile. Input: “set favorites” button in book details. Output: books stores in the user’s profile.
	
	
	Sharing via email: sharing book details via email. Input: sharing button in book details. Output: generate share URL link that ready to send via email. 





	\section{Non-functional Issues}
	%----------------------------------------Feiyu fill in here--------------------------
	%Types of Graphical User Interface (GUI) and Software tools to build GUI. Security, access control, ...etc



\end{document}
